---
# title: "Test-doc"
author: "BM"
date: "2023-07-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Learning how to use github with R 

Following this tutorial: https://resources.github.com/github-and-rstudio/


## Switching branch

In the terminal window in R: 

```{}
# Find out what branch you are on:
 git status
 
# Create a new branch
git status new-branch

# Move to that branch
git checkout new-branch

```

## Checking the status of your changed files

```{}
# Check the status of your branch 
git status new-branch 

# Happy with the changes and want to stage them?
git add .


```

## Commiting changes from the terminal

```{}
# Make a new commit
git commit -m "<COMMIT-MESSAGE>"

# Find out about previous commits
git log --oneline

# We can see changes between our branch and the main using
git diff --stat --summary main..new-branch

```

## Making the change this branch was designed for!: 

```{r, results='hide'}

plot(mtcars$mpg~mtcars$cyl)

```

## Now to merge with the main branch 

```{}
# run
git push -u origin new-branch

```
Now over to **github** to raise our branch as a pull request

## Tidy up the local copy
We made the merge on github fine, and deleted the new-branch branch, but as we are working on a local copy we need to now:
1) Move back to the main branch
2) Pull the changes from the main branch 
3) Delete the now defunct new-branch

```{}
# Move to the main 
git checkout main

# Pull the changes
git pull

# delete the branch
git branch -D new-branch
```